Process_OlisJazEmData

### 2024-01-09 Code/Process_OlisJazEmData.Rmd
Removed PurParRatio from this rmd and added to the merge rmd

# Calculate Photosynthetic Usable Radiation (PUR) from MC normalized emission and normalized Olis whole cell absorbance spectrums.  
```{r PUR}
OlisJazMetaPUR <- OlisJazMetaData %>%
    filter(OlisAbs_nm >= 400 &
           OlisAbs_nm <= 700) %>%
  mutate(PURAbsWholeCell_Norm440 = MC_NormEm * AbsNorm440) %>% 
  group_by(SampleID, E_days) %>% 
  mutate(SumPURAbsWholeCell_Norm440 = sum(MC_NormEm * AbsNorm440),
         CalcPur_ue = round(Par_ue * (SumPURAbsWholeCell_Norm440 / sum(MC_NormEm))),
         CalcPurParRatio = round(CalcPur_ue / Par_ue, 3)) %>% 
ungroup() %>% 
  select(-SumPURAbsWholeCell_Norm440)

@@

OlisJazMetaPUR <- OlisJazMetaPUR %>%
  group_by(Strain, WL) %>% 
  mutate(PurParRatio = (mean(CalcPurParRatio)))%>% 
ungroup()

OlisJazMetaPUR <- OlisJazMetaPUR %>%
  group_by(Strain, WL, Par_ue) %>% 
  mutate(Pur_ue = round(mean(CalcPur_ue)))%>% 
ungroup()  %>% 
  select(-c(CalcPurParRatio, CalcPur_ue))

>>>>

# Calculate Photosynthetic Usable Radiation (PUR) from MC normalized emission and normalized Olis whole cell absorbance spectrums.  
```{r PUR}
OlisJazMetaPUR <- OlisJazMetaData %>%
    filter(OlisAbs_nm >= 400 &
           OlisAbs_nm <= 700) %>%
  mutate(PURAbsWholeCell_Norm440 = MC_NormEm * AbsNorm440) %>% 
  group_by(SampleID, E_days) %>% 
  mutate(SumPURAbsWholeCell_Norm440 = sum(MC_NormEm * AbsNorm440),
         CalcPur_ue = round(Par_ue * (SumPURAbsWholeCell_Norm440 / sum(MC_NormEm)))) %>% 
ungroup() %>% 
  select(-SumPURAbsWholeCell_Norm440)

@@

OlisJazMetaPUR <- OlisJazMetaPUR %>%
  group_by(Strain, WL, Par_ue) %>% 
  mutate(Pur_ue = round(mean(CalcPur_ue)),
         PurParRatio = (Pur_ue / Par_ue))%>% 
ungroup()  %>% 
  select(-c(CalcPur_ue))
